
---
title: "Sex-Informed Prognostic Score: Results Overview"
author: "Mauricio Cuello Fredes"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

 **Overview**

This document summarizes the prognostic performance of the sex-informed 10-gene score derived using LASSO Cox regression on z-score normalized expression data. The score was tested across multiple cancer types and stratified patients into high- and low-risk groups based on survival outcomes.

 **Score Formulas**

10-Gene Score (including CGB8): `Score_10 = 尾1路Gene1 + 尾2路Gene2 + ... + 尾10路Gene10`  
9-Gene Score (excluding CGB8): `Score_9 = 尾1路Gene1 + 尾2路Gene2 + ... + 尾9路Gene9`

 **KaplanMeier Survival Curves**

```{r, results='asis'}
knitr::include_graphics("~/Desktop/OS_10gene.pdf")
knitr::include_graphics("~/Desktop/PFI_10gene.pdf")
```

 **Reproducibility**

- Model: `glmnet` with `set.seed(12345)`  
- Input: `LASSO_definitive_ethnicity_simplified.xlsx`  
- Script: `lasso_survival_pipeline.R`  
- Output: Desktop PDFs  
- R version: `r R.version.string`

 **Contact**  
Mauricio Cuello Fredes, Pontificia Universidad Cat贸lica de Chile  
锔 mcuello@uc.cl
